### 2012-04-20 docs/unit_tests/unit_tests.tex
add test_advect figures

@@

\begin{figure}[t] 
\centering
\includegraphics[height=1.8in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.8in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.8in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of the {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity field plus
  gradient of a scalar (x-component; center); and resulting velocity after projecting
  out the non-divergence free portion (x-component; right).  This is will slipwall
  boundary conditions on all sides, a 2-level grid with the left half refined and
  right half coarse, and the hgprojection tested.}
\end{figure}

>>>>

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/dens_2d_orig_density}
\includegraphics[height=1.9in]{\unitfigpath/dens_2d_ppm1_xp_final_density}
\includegraphics[height=1.9in]{\unitfigpath/dens_2d_ppm1_xp_final_abserror} 
%
\caption[Results of the {\tt test\_advect} unit test]{\label{fig:unit:advtest}
  Initial Gaussian density profile (left); density profile after
  advecting to the right for one period (center); absolute error
  between the final and initial density fields, showing the error in
  the advection scheme (right).}
\end{figure}

@@

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of the {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity field plus
  gradient of a scalar (x-component; center); and resulting velocity after projecting
  out the non-divergence free portion (x-component; right).  This is will slipwall
  boundary conditions on all sides, a 2-level grid with the left half refined and
  right half coarse, and the hgprojection tested.}
\end{figure}
